Competing Bandits: The Perils of Exploration under Competition

### 2018-08-31 paper/content/perf_in_iso.tex
Stopping for lunch :).

We start with a pilot experiment in which we investigate each algorithm's performance "in isolation": in a stand-alone bandit problem without the competition. We focus on reputation scores (\ie sliding window averages) generated by each algorithm.

First, we confirm that algorithms' performance is ordered as we'd expect:
    $\TS \gg \DEG \gg \DG$.
For a given algorithm and MAB instance

the reputation ordering of the algorithms is what we would expect according to the multi-armed bandit literature where, according to the mean reputation, $\TS > \DEG > DG$ for sufficiently large $t$. Second, we want to better understand what statistics of the priors we can look at in isolation in order to help us predict and understand what to expect in the competition game.

\begin{figure}
\caption{Mean Reputation Trajectories in Isolation}
\includegraphics[scale=0.35]{"figures/nih_iso_mean"}
\label{prelim_means}
\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of a given algorithm on a given instance and then average this value across all the runs. The shaded area display 95\% confidence intervals.}}
\end{figure}

Figure \ref{prelim_means} shows that the mean reputation ordering is as we would expect for the Needle In Haystack prior \footnote{The mean reputation ordering that we expect also holds for the other two priors and the results for those can be found in the supplementary material.}.

>>>>

We start with a pilot experiment in which we investigate each algorithm's performance "in isolation": in a stand-alone MAB problem without competition. We focus on reputation scores generated by each algorithm.

First, we confirm that algorithms' performance is ordered as we'd expect:
    $\TS \gg \DEG \gg \DG$.
For each algorithm and each MAB instance, we compute the mean reputation score at each round, averaged over all \MRVs. We plot the \emph{mean reputation trajectory}: how this score evolves over time. Figure \ref{prelim_means} shows such plot for the Needle In Haystack instance (for other MAB instances the plots are similar).

\begin{finding}
\textit{The mean reputation trajectories are arranged as predicted by prior work: 
    $\TS > \DEG > \DG$.}
\end{finding}

\begin{figure}
\caption{Mean Reputation Trajectories in Isolation. The shaded area displays 95\% confidence intervals.}
\includegraphics[scale=0.35]{"figures/nih_iso_mean"}
\label{prelim_means}
%\caption*{\tiny{Mean reputation trajectory The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of a given algorithm on a given instance and then average this value across all the runs. The shaded area display 95\% confidence intervals.}}
\end{figure}

Now we ask a more nuanced question: are the mean reputation trajectories the right statistic for our purposes? That is, how well do they predict the outcomes of the competition game?
